Self Regulation Ontology Retest Analyses

### 2018-08-06 code/SRO_Retest_Analyses.Rmd
changed noise ceilings plot to be print compatible

tmp %>%  
  ggplot(aes(value, fill=sample))+
  geom_density(alpha = 0.5, position='identity', color=NA)+
  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
  scale_fill_manual(breaks=c("boot","lit"),
                       labels=c("Empirical", "Literature"),
                      name="Predictor",
                      values = c("purple", "orange"))+
  xlab('Variance Explained')+
  ylab('Density')+
  xlim(0,1)+
  ylim(0,40)+
  theme(axis.title.x  = element_text(size=16),
        axis.text.x  = element_text(size=14),
        axis.title.y  = element_text(size=16),
        legend.title  = element_text(size=16),
        legend.text  = element_text(size=16))

>>>>

tmp %>%  
  ggplot(aes(value, fill=sample))+
  geom_density(alpha = 0.5, position='identity', color=NA)+
  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
  scale_fill_manual(breaks=c("boot","lit"),
                       labels=c("Empirical", "Literature"),
                      name="Predictor",
                      values = c("gray15", "gray75"))+
  xlab('Proportion of Variance in Literature Explained')+
  ylab('Density')+
  xlim(0,1)+
  ylim(0,40)+
  theme(axis.title.x  = element_text(size=12),
        axis.text.x  = element_text(size=12),
        axis.text.y  = element_text(size=12),
        axis.title.y  = element_text(size=12),
        legend.title  = element_text(size=12),
        legend.text  = element_text(size=12))
